Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-04-14 paper/main.tex
add references.bib & citations to manuscript

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{todonotes}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}

@@

\author{Christian O. Häusler\textsuperscript{1,2{*}}, Michael Hanke\textsuperscript{1}}
% https://www.nature.com/sdata/publish/for-authors#other-formats

\maketitle
\thispagestyle{fancy}
1. Psychoinformatics Lab, Institute of Neuroscience and Medicine, Brain \& Behaviour (INM-7), Research Centre Jülich, Jülich, Germany,
2. Institute of Systems Neuroscience, Medical Faculty, Heinrich Heine University, Düsseldorf, Germany
{*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)

\begin{abstract}
% Analysis Paper abstract: < 170 words
% no references are allowed:
% new analysis of existing data of interest to a broad section of our audience
% highlighting innovative examples of data reuse
% may be used to present compelling new findings and conclusions derived from published data.
% submissions using data previously published at Scientific Data are encouraged
% submissions should exemplify reproducible research by clearly describing all steps in the analysis
% providing supporting source code, and explaining how and where others may access all data underlying the analysis.
Intro: PPA as classic example for an visual area
Methods: fMRI data, studyforrest data set, general linear model
Results: significant clusters in PPA, RSC, individual results in x of 15 subjects
Conclusions: PPA nicht exclusively
\end{abstract}
% Intro + Discussion = main text ~  3,000 words.
% include figure providing schematic overview of the study and assay(s) design
% -> ist overkill; Paradigma ist mit "Film ab" wenig kompliziert.
\section{Introduction}
% Bzgl. Zitationen (lasse alles so lange wie möglich in Kbibtext's .bib-Datei): \cite{cite1, cite2}
% our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands).
Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g. viewing of landscapes, {epstein1998ppa}; or theory of mind {spunt2014validating}) to functional brain areas or networks. Brain mapping studies have traditionally employed small sets of carefully chosen, simplified stimuli to strictly control experimental conditions and facilitate functional isolation of brain areas. The disadvantage is that a limited number of simplified stimuli does not resemble our real-life experience and lacks external {westfall2016fixing} as well as ecological validity {hasson2004intersubject}. Additionally, brain mapping studies have traditionally averaged / usually average results across at least 10-15 subjects to improve the signal-to-noise-ratio (SNR). The disadvantage here is that the averaging approach does not  characterize brain functions at an individual level, a prerequisite for the application of brain imaging methods in individual diagnostics (cf. {dubois2016building})

@@

A classic example of a functional, higher-level visual area is the "parahippocampal place area" (PPA) {epstein1998ppa; epstein1999parahippocampal}. The PPA is located in the posterior parahippocampal gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral visual stream [mishkin1982contribution; goodale1992separate]. Increased hemodynamic activity in the PPA correlates with the perception of static pictures of landscapes or landmarks compared to pictures of tools or faces. According to the spatial layout hypothesis, the PPA is involved in processing the surface geometry of a visual stimulus and possibly in identifying scenes based on their spatial layout {epstein2010reliable}.
Results generalize at a group average level to a) mental imagination of landscapes {ocraven2000mental} and b) haptic exploration of scenes {wolbers2011modality}, \todo{this needs some more glue. the following is not just about spoken stimuli} whereas results of a study using spoken, place-related sentences were unclear \todo{should be more specific. unclear could mean 'not well described'} {aziz2008modulation}:
a) In a study conducted by {ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm. In a subsequent paradigm, participants were instructed to "form a vivid mental image" of the previously viewed pictures. The PPA showed increased activation during imagination of places compared to faces but the imagination tasks showed a smaller activation level compared to the perceptual task.

@@

b) In a block design study conducted by {wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from Lego bricks compared to haptically explored abstract geometric objects.

@@

c) To our knowledge only one study by {aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences. Sentences described generic or famous places (e.g. “The Taj Mahal faces a long thin reflecting pool”) or faces  (e.g. “Marylin Monroe has a large square jaw"). Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact. Surprisingly, activation in the left, but not right, PPA was significantly reduced \todo{reduced relative to what condition?} when participants listened to place-related sentences. Moreover, this effect was only observed in sentences involving famous places.

@@

In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information. This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general {aminoff2006parahippocampal} for a review). Independent(ly) from competing theories (s. {aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.

% coolness-faktor von natural stimuli ist in der Einleitung beinahe komplett raus
% data-driven analyses vs. theory-driven analyses ist komplett raus
% kann man in discussion bringen, muss man aber nicht ist ja dann offensichtlich
All studies reviewed above used a small set of carefully designed, simplified stimuli to strictly control experimental conditions. They further relied on / implemented explicit judgment-based tasks to keep participants alert and paying attention. Thus, they cannot / could answer the question how the PPA might behave under life-like conditions. Natural stimuli like movies [hasson2008neurocinematics; sonkusare2019naturalistic] or narratives [honey2012not-lost; lerner2011topographic; silbert2014coupled] offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
% hier wird GLM nicht explizit erwähnt; denke, muss nicht so spezifisch sein
In an early study [bartels2004mapping] manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}. These time points correlated with increased hemodynamic activity in the "fusiform face area" {kanwisher1997ffa} and "extrastriate body area"{downing2001body-area} respectively.
% hier wird ISC als solches nicht erwähnt
{hasson2004intersubject} took an inverse approach using a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}. fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) correlating movie frames. Results revealed that frames depicted indoor and outdoor scenes including buildings and open fields.
Both studies suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [<- der Schlusssatz ist aus hasson und bartels plagiiert]. Nevertheless, none of the reviewed study could investigate how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.

% ich habe einiges deiner Kommentare versucht einzubauen
% wenn dir etwas nicht explizit genug ist, fühl dich, frei mir auf die Finger zu hauen oder es vorzugsweise bei wenig Aufwand direkt umzuformulieren;
% bzgl. open source habe ich nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll. Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen
% MIH:
% 1. is such stimulus (more) suitable for distinguishing this cognitive process from others?
% 2. given its suitability how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
% 1) complex visual stimulation without a task, and
% 2) complex auditory stimulation without an explicit imagery task
% both aspects together can then be discussed in terms of the feasibility of (multi-dimensional) localizer development with naturalistic stimuli
% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
In this study, we analyze data of three publicly available datasets from the same set of 15 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}). We exploratorily investigate how the parrahippocampal gyrus responds to "spatially relevant" events embedded in a 2h audio-visual movie [hanke2016simultaneous] and it's audio-description of same length [hanke2014audiomovie]. Results are compared to PPA localizations that were obtained from a dedicated visual localizer experiment [sengupta2016extension]. Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task. We annotated events of the otherwise unknown temporal structure of both stimuli to be able to fit a theory-driven model. In/for the movie, we annotated different kinds of cinematographic cuts [haeusler2016annotation] as presumably "spatially relevant" events. Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut. In/for the audio-description, we annotated clues about the missing visual content given by the narrator {haeusler2019annotation}. We correlated regressors drawn from the annotations in order to detect possible/possibly confounded regressors that might prevent functional isolation of the PPA. In conformity to the analyses performed in the studies reviewed above, we submitted our regressors to a standard multi-level, voxel-wise general linear model (GLM). For practical reasons (+++es war a) viel einfacher als visual content zu annotieren und ist b) viel interessanter weil non-visual+++) and encouraged by {aziz2008modulation} and {aminoff2013role}, we focus on the audio-description as a possible life-like substitute to individually localize a "visual area" in visually impaired persons.

@@

\section{Methods}
% Ich habe die zwei Methodenteile gemerged und vor allem gekürzt;
% Einige Stellen sind aber sicherlich noch zu lange; denn im Zweifel habe ich es stehen gelassen
% Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below).
An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in {hanke2014audiomovie} and {hanke2016simultaneous; sengupta2016extension}

@@

\subsection{Participants}
% ggf. mit "Stimuli" zusammenfassen, weil sich das, dadurch dass die gleichen 15 in beiden Experimenten mitgemacht haben schwer prägnant trennen lässt.
In the first \todo{better to give them labels in the initial paragraph above, we will be referring to them quite a bit} study, fifteen participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description (Koop, Michalski, Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk, 2009) of the movie "Forrest Gump" (R. Zemeckis, Paramount Pictures, 1994) as an additional audio track for visually impaired listeners on Swiss public television. In the second study, the same 15 participants (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track. All participants reported to have normal hearing, normal or corrected-to-normal vision, and no known history of neurological disorders. In both studies, participants received monetary compensation and gave written informed consent for their participation and for public sharing of all obtained data in anonymized form. The studies had prior approval by the Ethics Committee of Otto-von-Guericke University of Magdeburg, Germany.

@@

\subsection{Stimuli}
% grey bars habe ich nicht erwähnt, obwohl sie - weil bei Lisas Stimuli überall anders - so viel Spaß gemacht haben
The movie's audio track and the audio-description are largely identical. The plot is carried by an off-screen voice of the main character Forrest Gump. The audio-description's male narrator additionally verbalizes essential aspects of the visual scenery when there is no dialog, off-screen voice or relevant sound in the audio track.
The audio-description was temporally aligned to the audio track of the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video, DE103519SV). A few scenes less relevant to the major plot were removed to create the "research cut" lasting $\approx$2h. Both stimuli were further processed (filtering, volume adjustments) to improve understandability / audibleness / audibility during MRI scanning. Finally, each stimulus was split into eight segments of approximately 15 minutes. Except for the first movie segment, each segment started with a snippet of at least six seconds immediately preceding the movie scene boundary used to split the segments. \todo{cite fig 3a from hanke2014}

\subsection{Procedure}
In both studies, participants filled out a questionnaire on their basic demographic information and familiarity with the audio-description or the movie. Participants were instructed to inhibit physical movements except for eye-movements, and otherwise to simply "enjoy the audiobook" or "enjoy the movie" respectively.
Audio-description and movie segments were presented in chronological order with four segments in two fMRI sessions respectively. \todo{possibly cut the rest of the section} At the start recording session(s), participants listened to music from the movie’s closing credits segment to individually determine optimal stimulus volume. Participants were instructed to "maximize the volume of the stimulus without it becoming unpleasantly loud or causing acoustic distortions by overdriving the loudspeaker hardware". % unterscheidet sich ggf. zwischen Hörspiel / Film oder kann ganz raus?
Between sessions, participants left the scanner for a break with a flexible duration. Structural images were obtained during the first study on a day different from the fMRI session.

\subsection{Stimulation setup}
Stimulation was implemented with PsychoPy v1.79 (with an early version of the MovieStim2 component later to be publicly released with \href{http://www.psychopy.org}{PsychoPy v1.81}; {peirce2007psychopy}) running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system [halchenko2012open].
% Einige Dinge können m.M.n. raus; insb. das in den []-Klammern
% habe es noch einmal drinnen gelassen, solltest Du die Dinge für wichtig halten
In the auditory study, visual instructions were presented on a rear-projection screen inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant’s visual field in order to prevent premature fatigue. [The screen contained a solid black "fixation" dot that faded in and out at the beginning and end of a movie segment.]
In the audio-visual study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to 13.7\% with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000). The movie was shown at a viewing distance of 63\,cm in 720\,p resolution at full width on a 1280 *1024\,pixel screen with 60\,Hz video refresh rate and screen dimension of 26.5 * 21.2\,cm, corresponding to 23.75*13.5 or 23.75*10.25 when considering only the movie content and excluding the horizontal gray bars].
% Hier hat es Unterschiede zwischen Hörspiel & Film geben? habe es wie folgt zusammengefasst; im Zweifel ist es eh noch zu ausführlich
Auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; {baumgart1998electrodynamic}) that reduced the scanner noise by at least 20–30 dB. Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.

\subsection{fMRI data acquisition}
In both studies, a total of 3599 volumes were recorded for each participant (451, 441, 438, 488, 462, 439, 542 and 338 volumes for movie segment 1–8 respectively).
In the auditory study, a whole-body 7-Tesla Siemens MAGNETOM magnetic resonance scanner equipped with a local circularly polarized head transmit and a 32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 22\,ms echo time, 0.78\,ms echo spacing, 1488\,Hz/Px bandwidth, generalized autocalibrating partially parallel acquisition, acceleration factor 3, 24 Hz/Px bandwidth in phase encoding direction)  using 36 axial slices (thickness 1.4\,mm, 1.4 x 1.4\,mm in-plane resolution, 224\,mm field-of-view, anterior-to-posterior phase encoding direction) with a 10 percent inter-slice gap were recorded in ascending order. Slices were oriented to include the ventral portions of frontal and occipital cortex while minimizing intersection with the eyeballs. The field-of-view was centred on the approximate location of Heschl's gyrus.
% EPI images were online-corrected for motion and geometric distortions [Oh, S. et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]. Auxiliary scans for slice alignment and motion- and distortion-correction were performed at the beginning of the first fMRI recording session and also after the break at the start of the recording for the second half of the movie.
In the audio-visual study, a whole-body 3 Tesla Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 30\,ms echo time, 90 DEGREE flip angle, 1943\,Hz/Px bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2). 35 axial slices (thickness 3.0\,mm, 10 \% inter-slice gap) with 80*80 voxels (3.0*3.0 mm of in-plane resolution), 240\,mm mm field-of-view (FoV) and an anterior-to-posterior phase encoding direction were recorded in ascending order. Philips’ “SmartExam” was used to automatically position slices in AC-PC orientation such that the topmost slice was located at the superior edge of the brain.

\subsection{Stimulus Annotation}
% wurde unter "Regressoren" zu Beginn der 1st-lvl-Analyse verschoben

>>>>

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{todonotes}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

\author{Christian~O.~Häusler\textsuperscript{1,2{*}}, Michael Hanke\textsuperscript{1,2}}
% https://www.nature.com/sdata/publish/for-authors#other-formats

\maketitle
\thispagestyle{fancy}

1. Psychoinformatics Lab, Institute of Neuroscience and Medicine, Brain \& Behaviour (INM-7), Research Centre Jülich, Jülich, Germany,
2. Institute of Systems Neuroscience, Medical Faculty, Heinrich Heine University, Düsseldorf, Germany
{*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)

\begin{abstract}
% < 170 words
% new analysis of existing data
% of interest to a broad section of our audience
% highlighting innovative examples of data reuse
% may be used to present compelling new findings & conclusions derived from published data.
% submissions should exemplify reproducible research by clearly describing all steps in the analysis
% providing supporting source code, and explaining how and where others may access all data underlying the analysis.
Intro: PPA as classic example for an visual area
Methods: fMRI data, studyforrest data set, general linear model
Results: significant clusters in PPA, RSC, individual results in x of 15 subjects
Conclusions: PPA nicht exclusively
\end{abstract}
% Intro + Discussion = main text ~ 3,000 words.
% include figure providing schematic overview of the study and assay(s) design
% -> ist overkill; Paradigma ist mit "Film ab" wenig kompliziert.
\section{Introduction}
% our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands).

% yeah, whatever. Arbeite erstmal mit der references.bib
% und habe oben '\usepackage{natbib}' eingefügt
Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g. viewing of landscapes, \citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to functional brain areas or networks. Brain mapping studies have traditionally employed small sets of carefully chosen, simplified stimuli to strictly control experimental conditions and facilitate functional isolation of brain areas.
The disadvantage is that a limited number of simplified stimuli does not resemble our real-life experience and lacks external \citep{westfall2016fixing} as well as ecological validity \citep{hasson2004intersubject}.
Additionally, brain mapping studies have traditionally averaged / usually average results across at least 10-15 subjects to improve the signal-to-noise-ratio (SNR). The disadvantage here is that the averaging approach does not  characterize brain functions at an individual level, a prerequisite for the application of brain imaging methods in individual diagnostics (cf. \citep{dubois2016building})

@@

A classic example of a functional, higher-level visual area is the ``parahippocampal place area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}. The PPA is located in the posterior parahippocampal gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral visual stream \citep{mishkin1982contribution, goodale1992separate}. Increased hemodynamic activity in the PPA correlates with the perception of static pictures of landscapes or landmarks compared to pictures of tools or faces.
According to the spatial layout hypothesis, the PPA is involved in processing the surface geometry of a visual stimulus and possibly in identifying scenes based on their spatial layout \citep{epstein2010reliable}.
Results generalize at a group average level to a) mental imagination of landscapes \citep{ocraven2000mental} and b) haptic exploration of scenes \citep{wolbers2011modality}, \todo{this needs some more glue. the following is not just about spoken stimuli} whereas results of a study using spoken, place-related sentences were unclear \todo{should be more specific. unclear could mean 'not well described'} \citep{aziz2008modulation}:
a) In a study conducted by \citep{ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm.
In a subsequent paradigm, participants were instructed to ``form a vivid mental image'' of the previously viewed pictures. The PPA showed increased activation during imagination of places compared to faces but the imagination tasks showed a smaller activation level compared to the perceptual task.

@@

b) In a block design study conducted by \citep{wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from Lego bricks compared to haptically explored abstract geometric objects.

@@

c) To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences. Sentences described generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting pool'') or faces  (e.g. ``Marylin Monroe has a large square jaw''). Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact. Surprisingly, activation in the left, but not right, PPA was significantly reduced \todo{reduced relative to what condition?} when participants listened to place-related sentences. Moreover, this effect was only observed in sentences involving famous places.

@@

In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information. This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general \citep{aminoff2006parahippocampal} for a review). Independent(ly) from competing theories (s. \citep{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.

% coolness-faktor von natural stimuli ist in der Einleitung beinahe komplett raus
% data-driven analyses vs. theory-driven analyses ist komplett raus
% kann man in discussion bringen, muss man aber nicht ist ja dann offensichtlich
All studies reviewed above used a small set of carefully designed, simplified stimuli to strictly control experimental conditions. They further relied on / implemented explicit judgment-based tasks to keep participants alert and paying attention. Thus, they cannot / could answer the question how the PPA might behave under life-like conditions. Natural stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012notlost, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
% hier wird GLM nicht explizit erwähnt; denke, muss nicht so spezifisch sein
In an early study \citep{bartels2004mapping} manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}. These time points correlated with increased hemodynamic activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively.
% hier wird ISC als solches nicht erwähnt
\citep{hasson2004intersubject} took an inverse approach using a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}. fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) correlating movie frames. Results revealed that frames depicted indoor and outdoor scenes including buildings and open fields.
Both studies suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [<- der Schlusssatz ist aus hasson und bartels plagiiert]. Nevertheless, none of the reviewed study could investigate how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.

% ich habe einiges deiner Kommentare versucht einzubauen
% wenn dir etwas nicht explizit genug ist, fühl dich, frei mir auf die Finger zu hauen oder es vorzugsweise bei wenig Aufwand direkt umzuformulieren;
% bzgl. open source habe ich nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll. Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen
% MIH:
% 1. is such stimulus (more) suitable for distinguishing this cognitive process from others?
% 2. given its suitability how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
% 1) complex visual stimulation without a task, and
% 2) complex auditory stimulation without an explicit imagery task
% both aspects together can then be discussed in terms of the feasibility of (multi-dimensional) localizer development with naturalistic stimuli
% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
In this study, we analyze data of three publicly available datasets from the same set of 15 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}). We exploratorily investigate how the parrahippocampal gyrus responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and it's audio-description of same length \citep{hanke2014audiomovie}. Results are compared to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}. Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task. We annotated events of the otherwise unknown temporal structure of both stimuli to be able to fit a theory-driven model. In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016annotation} as presumably ``spatially relevant'' events. Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut. In/for the audio-description, we annotated clues about the missing visual content given by the narrator \citep{haeusler2020spechanno}. We correlated regressors drawn from the annotations in order to detect possible/possibly confounded regressors that might prevent functional isolation of the PPA. In conformity to the analyses performed in the studies reviewed above, we submitted our regressors to a standard multi-level, voxel-wise general linear model (GLM). For practical reasons (+++es war a) viel einfacher als visual content zu annotieren und ist b) viel interessanter weil non-visual+++) and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like substitute to individually localize a ``visual area'' in visually impaired persons.

@@

\section{Methods}
% Ich habe die zwei Methodenteile gemerged und vor allem gekürzt;
% Einige Stellen sind aber sicherlich noch zu lange; denn im Zweifel habe ich es stehen gelassen
% Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below).
An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in \citep{hanke2014audiomovie} and \citep{hanke2016simultaneous, sengupta2016extension}

@@

\subsection{Participants}
% ggf. mit "Stimuli" zusammenfassen, weil sich das, dadurch dass die gleichen 15 in beiden Experimenten mitgemacht haben schwer prägnant trennen lässt.
In the first \todo{better to give them labels in the initial paragraph above, we will be referring to them quite a bit} study, fifteen participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description (Koop, Michalski, Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk, 2009) of the movie ``Forrest Gump'' (R. Zemeckis, Paramount Pictures, 1994) as an additional audio track for visually impaired listeners on Swiss public television. In the second study, the same 15 participants (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track. All participants reported to have normal hearing, normal or corrected-to-normal vision, and no known history of neurological disorders. In both studies, participants received monetary compensation and gave written informed consent for their participation and for public sharing of all obtained data in anonymized form. The studies had prior approval by the Ethics Committee of Otto-von-Guericke University of Magdeburg, Germany.

@@

\subsection{Stimuli}
% grey bars habe ich nicht erwähnt, obwohl sie - weil bei Lisas Stimuli überall anders - so viel Spaß gemacht haben
The movie's audio track and the audio-description are largely identical. The plot is carried by an off-screen voice of the main character Forrest Gump.
The audio-description's male narrator additionally verbalizes essential aspects of the visual scenery when there is no dialog, off-screen voice or relevant sound in the audio track.
The audio-description was temporally aligned to the audio track of the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video, DE103519SV).A few scenes less relevant to the major plot were removed to create the ``research cut'' lasting $\approx$2h. Both stimuli were further processed (filtering, volume adjustments) to improve understandability / audibility during MRI scanning.
Finally, each stimulus was split into eight segments of approximately 15 minutes. Except for the first movie segment, each segment started with a snippet of at least six seconds immediately preceding the movie scene boundary used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}

\subsection{Procedure}
In both studies, participants filled out a questionnaire on their basic demographic information and familiarity with the audio-description or the movie.
Participants were instructed to inhibit physical movements except for eye-movements, and otherwise to simply "enjoy the audiobook" or "enjoy the movie" respectively.
Audio-description and movie segments were presented in chronological order with four segments in two fMRI sessions respectively.
\todo{possibly cut the rest of the section} At the start recording session(s), participants listened to music from the movie’s closing credits segment to individually determine optimal stimulus volume. Participants were instructed to ``maximize the volume of the stimulus without it becoming unpleasantly loud or causing acoustic distortions by overdriving the loudspeaker hardware''.
% unterscheidet sich ggf. zwischen Hörspiel / Film oder kann ganz raus?
Between sessions, participants left the scanner for a break with a flexible duration. Structural images were obtained during the first study on a day different from the fMRI session.

\subsection{Stimulation setup}
Stimulation was implemented with PsychoPy v1.79 (with an early version of the MovieStim2 component later to be publicly released with \href{http://www.psychopy.org}{PsychoPy v1.81}; \citep{peirce2007psychopy}) running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
% Einige Dinge können m.M.n. raus; insb. das in den []-Klammern
% habe es noch einmal drinnen gelassen, solltest Du die Dinge für wichtig halten
In the auditory study, visual instructions were presented on a rear-projection screen inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.).
During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant’s visual field in order to prevent premature fatigue.
[The screen contained a solid black ``fixation'' dot that faded in and out at the beginning and end of a movie segment.]
In the audio-visual study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to 13.7\% with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
The movie was shown at a viewing distance of 63\,cm in 720\,p resolution at full width on a 1280 *1024\,pixel screen with 60\,Hz video refresh rate and screen dimension of 26.5 * 21.2\,cm, corresponding to 23.75*13.5 or 23.75*10.25 when considering only the movie content and excluding the horizontal gray bars].
% Hier hat es Unterschiede zwischen Hörspiel & Film geben? habe es wie folgt zusammengefasst; im Zweifel ist es eh noch zu ausführlich
Auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by at least 20–30 dB. Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.

\subsection{fMRI data acquisition}
In both studies, a total of 3599 volumes were recorded for each participant (451, 441, 438, 488, 462, 439, 542 and 338 volumes for movie segment 1–8 respectively).
In the auditory study, a whole-body 7-Tesla Siemens MAGNETOM magnetic resonance scanner equipped with a local circularly polarized head transmit and a 32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 22\,ms echo time, 0.78\,ms echo spacing, 1488\,Hz/Px bandwidth, generalized autocalibrating partially parallel acquisition, acceleration factor 3, 24 Hz/Px bandwidth in phase encoding direction) using 36 axial slices (thickness 1.4\,mm, 1.4 x 1.4\,mm in-plane resolution, 224\,mm field-of-view, anterior-to-posterior phase encoding direction) with a 10 percent inter-slice gap were recorded in ascending order.
Slices were oriented to include the ventral portions of frontal and occipital cortex while minimizing intersection with the eyeballs. The field-of-view was centred on the approximate location of Heschl's gyrus.
% EPI images were online-corrected for motion and geometric distortions [Oh, S. et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]. Auxiliary scans for slice alignment and motion- and distortion-correction were performed at the beginning of the first fMRI recording session and also after the break at the start of the recording for the second half of the movie.
In the audio-visual study, a whole-body 3 Tesla Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 30\,ms echo time, 90 DEGREE flip angle, 1943\,Hz/Px bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2). 35 axial slices (thickness 3.0\,mm, 10\% inter-slice gap) with 80*80 voxels (3.0*3.0 mm of in-plane resolution), 240\,mm mm field-of-view (FoV) and an anterior-to-posterior phase encoding direction were recorded in ascending order. Philips’ “SmartExam” was used to automatically position slices in AC-PC orientation such that the topmost slice was located at the superior edge of the brain.
